A-maze: Easier measurement of incremental processing

### 2020-05-27 Analysis/nat_stories.Rmd
gitignore

>>>>

ggplot(for_plot, aes(x=pct_correct, y=mean_rt))+
  geom_point()+
  scale_color_viridis(discrete=T)+
  labs(x="Fraction words selected correctly",
       y="Mean Reaction Time (ms)",
       color="?s correct")+
  coord_cartesian(xlim=c(0.4,1), ylim=c(0,1600))+
    #scale_color_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
  guides(color=FALSE)

ggsave("../error.jpg", width=5, height=3, unit="in")

### 2020-05-27 Analysis/nat_stories_lms.Rmd
gitignore

@@

```
```{r}

@@

>>>>

data_post_only <- data_no_first %>% filter(rt>100 & rt<5000) %>% 
  filter(!after_mistake==0) %>% 
    select(subject, word_num, word, rt, sentence, type)

@@

labelled_post_only <- data_post_only %>% inner_join(past_word, by=c("word_num", "word", "sentence")) %>%
  filter(word_num>1) %>% 
select(rt, subject, Word_In_Story_Num, Story_Num,txl_surp,ngram_surp,grnn_surp, freq,length,
         txl_center, ngram_center,grnn_center,freq_center, length_center, starts_with("past")) %>% 
  mutate(Word_ID=as_factor(str_c(Story_Num, Word_In_Story_Num, sep="_"))) %>% 
  select(-Word_In_Story_Num, -Story_Num)
```

@@

ggsave("../Papers/gam2.pdf", width=3.5, height=2, unit="in")

for_graph_3 <- labelled_post_only %>% 
  select(rt, txl_surp, ngram_surp, grnn_surp, past_txl, past_grnn, past_ngram) %>%
  pivot_longer(cols=`txl_surp`:`past_ngram`,names_to="label", values_to="data") %>% 
  mutate(type=case_when(
         label %in% c("past_ngram", "past_txl", "past_grnn")~"Previous",
         T~"Current"),
         model=case_when(
           label %in% c("txl_surp", "past_txl")~"TXL",
           label %in% c("grnn_surp", "past_grnn")~"GRNN",
           T ~ "5-gram"
         ))

ggplot(for_graph_3, aes(x=data, y=rt))+
         geom_smooth(method="gam",formula= y~s(x, bs="cr", k=20),color="black")+
         facet_grid(type~model)+
        labs(x="Surprisal (bits)", y="Reaction Time (ms)")

ggsave("../Papers/gam3.pdf", width=3.5, height=2, unit="in")

### 2020-05-27 Papers/lab_meeting_2020.tex
gitignore

In Boyce et al. (2020) we replicate Witzel et al. (2012)
\begin{itemize}
	\item Witzel et al (2012): Comparison of eye-tracking, SPR, L-maze, G-maze (all in-lab)
	\item Got materials and data from Witzel
	\item We run SPR, L-maze, and G-maze on MTurk
\end{itemize}
\end{frame}

@@

\begin{frame}{Can we use LMs to choose distractors?} Idea: Use high surprisal according to LM as a proxy for really bad in context
\medskip

@@

\begin{itemize}
	\item Model the target sentence word by word \pause
	\item At each position, choose a high surprisal word
\end{itemize}
\medskip
\pause
Want quality control on distractors
\pause
\begin{itemize}
	\item Restrict to a list of possible distractors
	\item Only consider distractors of same length, frequency as target wrd
	\item Check distractors until we find one with high surprisal
	\item Match to real word punctuation
\end{itemize}

@@

@@

{\large Option 1: Choose better distractors.}
\begin{itemize}
	\item Tweak thresholds of distractor selection.
	\item Could search for optimal thresholds.
	\item Could manually check and fix distractors.
\end{itemize}

@@

{\large Option 2: Be forgiving.}
\begin{itemize}
	\item Just don't terminate on mistakes.
	\item Instead have participant correct mistake and continue. 
	\item Easy to implement in Ibex framework.
	\end{itemize}
\end{frame}

@@

{\large The ``solution'' to our problems!}

@@

	\end{column} \pause 
	\begin{column}{0.7\textwidth} 
		\begin{center}
			\begin{itemize}
				\item Can be toggled in Ibex
				\item Have all the data
				\item Identify bad participants v bad distractors
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}
\medskip
\pause

@@

\section{Experiment 2} %TODO: Needs work from here on!

@@

Use 3 LMs to estimate surprisal: smoothed 5-gram, Gulordava RNN, Transformer-XL (Gulordava et al. 2018, Dai et al. 2019)

\includegraphics[width=.9\textwidth]{gam.pdf}

Only on single token words.

@@

\begin{frame}{What about post-mistake data?}
Exclude data from mistakes or the two words after a mistake.

@@

\begin{frame}{Result Summary}
\begin{itemize}
	\item People will read in the Maze task for 15-20 minutes
	\item It's possible to comprehend during Maze
	\item Distractors are generally good enough
	\item Find expected RT patterns
	\item Very little spillover
\end{itemize}
\end{frame}
\section{Conclusion}

\begin{frame}{Use A-maze!}
Easy to use!
\begin{itemize}
	\item Runs on command line 
	\item Match distractors across minimal pair sentences
	\item Customize surprisal thresholds, vocabulary lists
	\item Can output pre-formatted for Ibex
	\item Lots of documentation at vboyce@github.io/Maze
\end{itemize}
\medskip
\pause
\end{frame}

\begin{frame}{Use A-maze!}
Contribute to A-maze!:
\begin{itemize}
	\item Written in Python 3
	\item Add more language models
	\item Add more frequency sources
	\item Extend to non-English languages
\end{itemize}

@@

\textcolor{ForestGreen}{\large Documentation: vboyce@github.io/Maze}

@@

\item Sample task: syntaxgym.org:666
\end{itemize}
\end{frame}

>>>>

Test by replicating Witzel et al. (2012)
\begin{itemize}
	\item Witzel et al (2012): Comparison of eye-tracking, SPR, L-maze, G-maze (all in-lab)
	\item Got materials and data from Witzel
	\item We run SPR, L-maze, and G-maze on MTurk
\end{itemize}
\end{frame}

@@

\begin{frame}{Can we use LMs to choose distractors?}

Use high surprisal according to LM as a proxy for bad in context
\medskip

@@

\begin{itemize}
	\item Model the target sentence word by word \pause
	\item At each position, choose a high surprisal word
\end{itemize}
\medskip
\pause
Want quality control on distractors
\pause
\begin{itemize}
	\item Restrict to a list of possible distractors \pause
	\item Only consider distractors of same length, frequency as target word \pause
	\item Check distractors until we find one with high surprisal \pause
\end{itemize}

@@

\section{Experiment 2}

@@

{\large Option 1: Choose better distractors.} \pause
\begin{itemize}
	\item Tweak thresholds of distractor selection. \pause
	\item Could search for optimal thresholds. \pause
	\item Could manually check and fix distractors. 
\end{itemize}

@@

{\large Option 2: Be forgiving.} \pause
\begin{itemize}
	\item Just don't terminate on mistakes. \pause
	\item Instead have participant correct mistake and continue.
	\end{itemize}
\end{frame}

@@

{\large The ``solution'' to our problems!} \pause

@@

	\end{column} \pause 
	\begin{column}{0.7\textwidth} 
		\begin{center}
			\begin{itemize}
				\item Easily implemented as a toggle in Ibex \pause
				\item Have all the data \pause
				\item Identify bad participants v bad distractors 
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}
\medskip
\pause

@@

 %TODO: Needs work from here on!

@@

Use 3 LMs to estimate surprisal: smoothed 5-gram, Gulordava RNN, Transformer-XL (Gulordava et al. 2018, Dai et al. 2019)
\pause

Fit GAMs on pre-error data.
\begin{itemize}
	\item Limit to single-token words.
	\item Fit to both current and past word surprisal.
\end{itemize}

@@

\begin{frame}{Surprisal Effects}
\includegraphics[width=.9\textwidth]{gam.pdf}	
\end{frame}
\begin{frame}{What about post-mistake data?}
Exclude data from mistakes or the two words after a mistake.

@@

\begin{frame}{Summary}
\begin{itemize}\pause
	\item People will read in the Maze task for 15-20 minutes \pause
	\item It's possible to comprehend during Maze \pause
	\item Distractors are generally good enough \pause
	\item Find expected RT patterns \pause
	\item Very little spillover
\end{itemize}
\end{frame}
\section{Conclusion}

\begin{frame}{Use A-maze!}
Easy to use! \pause
\begin{itemize}
	\item Runs on command line \pause
	\item Match distractors across minimal pair sentences \pause
	\item Customize surprisal thresholds, vocabulary lists \pause
	\item Can output pre-formatted for Ibex
\end{itemize}
\medskip
\pause
\end{frame}

\begin{frame}{Use A-maze!} \pause
Contribute to A-maze:
\begin{itemize}
	\item Written in Python 3 \pause
	\item Interface with other language models \pause
	\item Add more frequency sources \pause
	\item Extend to non-English languages
\end{itemize}

@@

\textcolor{ForestGreen}{\large Documentation: vboyce.github.io/Maze}

@@

\item Sample task: syntaxgym.org:666

\item Paper: psyarxiv.com/b7nqd/
\end{itemize}
\end{frame}
